Embedding Dimension of Polyhedral Losses

### 2020-01-30 colt-20/embed-dim.tex
Added figures for Bo's proof of abstain not being 2-embeddable.

\begin{lemma} \label{lemma:180-degree-no-three}
  There is no feasible solution to the QFP for $\gamma_{\bot}$ and $\ell_{1/2}$ where three vectors $v_i,v_j,v_m$ lie strictly within a halfspace through the origin (i.e. all within $180^{\circ}$ of each other).
\end{lemma}
\begin{proof}
  Let three of the vectors be given, lying strictly inside a halfspace, and label them clockwise clockwise as $v_1,v_2,v_3$.
  WLOG suppose $v_1$ points vertically ``up'', as in Figure \ref{bo:todo}.
  By Lemma \ref{lemma:unique-spot-xiji}, the possible locations of the following points are all uniquely determined: $x^{ij}_i, x^{ij}_j$ for $(i,j) \in \{(1,2),(1,3),(2,3)\}$.
  Both points $x^{12}_1$ and $x^{13}_1$ lie on the line $\inprod{v_1}{x} = -1$, i.e. a horizontal line below the origin.
  We have constraints $\inprod{v_2}{x^{12}_1} = 1$ and $\inprod{v_2}{x^{13}_1} \leq 1$.
  This implies $x^{13}_1$ is left of $x^{12}_1$ on the line $\inprod{v_1}{x} = 1$. 
  But the symmetric constraints $\inprod{v_3}{x^{13}_1} \leq \jessie{=?} 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$ imply that $x^{12}_1$ is left of $x^{13}_1$ on the line.
  This implies we must have $x^{12}_1 = x^{13}_1$.

@@

\begin{proposition}
	The abstain loss $\ell_{1/2}$ with $n=5$ is not $2$-embeddable.
\end{proposition}
\begin{proof}
  Let any $5$ vectors be given, numbered clockwise.
  $v_1,v_2,v_3$ cannot lie in a cone of strictly less than $180^{\circ}$, as this would contradict \bo{the previous}.
  So the clockwise angle between $v_1$ and $v_3$ is at least $180^{\circ}$.
  Since there are no duplicates, this implies that the clockwise angle between $v_4$ and $v_1$, which includes $v_5$, is strictly less than $180^{\circ}$.
  This contradicts \bo{the previous}.
\end{proof}

>>>>

\begin{figure}
	\begin{minipage}{0.3\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{tikz/v1}
		\caption{Example of $v_1$.}
		\label{fig:v1}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{tikz/qp-must-intersect-line-same-spot}
		\caption{If $x^{12}_1 \neq x^{13}_1$, we have a contradiction.}
		\label{fig:qp-must-intersect-line-same-spot}
	\end{minipage}
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/qp-line-intersect-contradiction}
	\caption{The intersection of $\inprod{v_2}{x} = -1$ and $\inprod{v_3}{x} = 1$ occurs outside the region $\inprod{v_1}{x} \in [-1,1]$.}
	\label{fig:qp-line-intersect-contradiction}
\end{minipage}
\hfill

\end{figure}

\begin{lemma} \label{lemma:180-degree-no-three}
  There is no feasible solution to the QFP for $\gamma_{\bot}$ and $\ell_{1/2}$ where three vectors $v_i,v_j,v_m$ lie strictly within a halfspace through the origin (i.e. all within $180^{\circ}$ of each other).
\end{lemma}
\begin{proof}
  Let three of the vectors be given, lying strictly inside a halfspace, and label them clockwise clockwise as $v_1,v_2,v_3$.
  WLOG suppose $v_1$ points vertically ``up'', as in Figure \ref{fig:v1}.
  By Lemma \ref{lemma:unique-spot-xiji}, the possible locations of the following points are all uniquely determined: $x^{ij}_i, x^{ij}_j$ for $(i,j) \in \{(1,2),(1,3),(2,3)\}$.
  Both points $x^{12}_1$ and $x^{13}_1$ lie on the line $\inprod{v_1}{x} = -1$, i.e. a horizontal line below the origin.
  We have constraints $\inprod{v_2}{x^{12}_1} = 1$ and $\inprod{v_2}{x^{13}_1} \leq 1$.
  This implies $x^{13}_1$ is left of $x^{12}_1$ on the line $\inprod{v_1}{x} = 1$. 
  But the symmetric constraints $\inprod{v_3}{x^{13}_1} \leq \jessie{=?} 1$ and $\inprod{v_3}{x^{12}_1} \leq 1$ imply that $x^{12}_1$ is left of $x^{13}_1$ on the line.
  This implies we must have $x^{12}_1 = x^{13}_1$.

@@

\begin{proposition}
	The abstain loss $\ell_{1/2}$ with $n=5$ is not $2$-embeddable.
\end{proposition}
\begin{proof}
  Let any $5$ vectors be given, numbered clockwise.
  $v_1,v_2,v_3$ cannot lie in a cone of strictly less than $180^{\circ}$, as this would contradict Lemma~\ref{lemma:180-degree-no-three}.
  So the clockwise angle between $v_1$ and $v_3$ is at least $180^{\circ}$.
  Since there are no duplicates, this implies that the clockwise angle between $v_4$ and $v_1$, which includes $v_5$, is strictly less than $180^{\circ}$.
  This contradicts Lemma~\ref{lemma:180-degree-no-three}.
\end{proof}
